Collective behavior of Suspended Janus Particles via an Integral Equation Method

### 2022-05-12 doc/PRF2022/PRF_main.tex
update

@@

Notice that for this simulation, the center of mass position of the initial configuration is not at the origin and it is slightly to the right of the origin. Therefore, the result has shown that the structure stretching occurs earlier that the case when we shift the center of mass position to the origin.

>>>>

\begin{figure}
  \begin{center}
  \includegraphics[width=0.5\textwidth]{Relax_Energy.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy} Energy profile for all three boundary conditions.}
\end{figure}

@@

Notice that for this simulation, the center of mass position of the initial configuration is not at the origin and it is slightly to the right of the origin. Therefore, the result has shown that the structure stretching occurs earlier than the case when we shift the center of mass position to the origin.
